\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[margin=2.9cm]{geometry}
\usepackage{array}
\usepackage{longtable}
\usepackage{amssymb}
\usepackage{enumitem} % For customizing itemize lists
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{dashrule}
\usepackage[most]{tcolorbox}
\usepackage{xcolor}
\usepackage{colortbl}

\title{The Consistency Key: A Full Risk Management Model\\ for Forex \& Futures}
\author{MR5OBOT \\ \textit{"Risk Management is your only shield against ultimate failure.."}}
\date{\today}


\begin{document}
\maketitle
% \pagestyle{fancy}
% \tableofcontents
\noindent\hdashrule[0.2ex]{\linewidth}{0.1pt}{1mm} 

\newtcolorbox{notebox}{
    colback=gray!8, % Light grey background color
    colframe=gray!10, % Border color
    arc=0mm, % No rounded corners
    boxrule=0.2mm, % Border thickness
    left=2mm, % Padding on the left side
    right=2mm, % Padding on the right side
    top=1mm,
    bottom=1.5mm,
}

% Define a new tcolorbox style for the "Notes" section
\newtcolorbox{notesbox}{
    colback=yellow!30, % Light yellow background color
    colframe=yellow!10, % Slightly darker yellow border color
    boxrule=0.5pt, % Border thickness
    arc=2pt, % Rounded corners
    left=5pt, % Left padding
    right=5pt, % Right padding
    top=3pt, % Top padding
    bottom=3pt % Bottom padding
}

\newtcolorbox{violetbox}{
    colback=violet!10, % Light yellow background color
    colframe=violet!10, % Slightly darker yellow border color
    boxrule=0.5pt, % Border thickness
    arc=2pt, % Rounded corners
    left=5pt, % Left padding
    right=5pt, % Right padding
    top=3pt, % Top padding
    bottom=3pt % Bottom padding
}


\section*{The missing piece of the puzzel}
\begin{notebox}
| What has your Trading results shown you over the course of your career as a Trader? Are you atruggling?  have you seen your account experience devastating drawdown or worse... blow it out? I purposely placed this topic at the beginning ogf the core material as I believe it is the most vital component to long term success in trading Forex... or any other asset class! \\
  \\ \indent{ I am confident the piece of the puzzel you are looking for is Risk Management. Have you risked more than 1\% of your total equity on any one trade? How about just about every one of them? Have you tried on any over-leverage your account to make the losses back right away... only to find it resulted in steeper losses and deeper in depression?}  \\
  \\ \indent{ At the top of the list of crucial components to seccessful and cosistent trading is the concept of Risk Management.  Riks Management is basically divided into two core principles... Money Management an Trade Management .  These areas are far greater in importance than your treasured little Trading System or patterns.}\
\end{notebox}

\subsubsection*{What Does \underline{Risk Management} Really Mean?}
\begin{violetbox}
\small It's The amount of Risk the Trader is wailling to assume. It should be limited to 1\% of total equity or less. To calculate the Risk per trade use the following formula...
\end{violetbox}

\begin{itemize}
  \item \textbf{Account balance} : $ 10000\$ $
  \item  \textbf{Percentage Risk} : $ 1\% $ 
\end{itemize}

\begin{center}
   \textbf{ \underline{The Formula}}
\vspace{0.1cm}
  \[ ( 10000\$ * 1\% ) = \frac{10000}{0.01} = 100\$ \]
\end{center}

\vspace{0.2cm}
\begin{notesbox}
  \small{  So we have defined our risk per trade as 1\% | 100\$ of total equity 10000\$ \\
  Then the next section will cover \underline{Risk Reward Ratio}}
\end{notesbox}

\footnote{Twitter [ @MR-5OBOT ]}
\newpage 

\renewcommand{\arraystretch}{1.5} % table padding vertical space 
\setlength{\tabcolsep}{10pt} % table padding horizontal space

\begin{tabular}{|c|c|c|}
  \cline{1-2}
 \rowcolor{gray!30} Equity & Risk 1\% \\
  \hline 
  \$ 9,900.00 & NYKZN & Loss 1 \\  
  \hline 
  \$ 9,800.00 & NYKZN & Loss 2 \\  
  \hline            
  \$ 9,700.00 & NYKZN & Loss 3 \\  
  \hline            
  \$ 9,600.00 & NYKZN & Loss 4 \\  
  \hline            
  \$ 9,600.00 & NYKZN & Loss 5 \\  
  \hline            
  \$ 9,500.00 & NYKZN & Loss 6 \\  
  \hline            
  \$ 9,400.00 & NYKZN & Loss 7 \\  
  \hline            
  \$ 9,300.00 & NYKZN & Loss 8 \\  
  \hline
\end{tabular}

\newpage
\subsection*{Position Sizing}
% \begin{itemize} 
%   \item Risk per Trade = 1\% Max        \vspace{0.2cm}
%   \item Max Daily Trades = 2 Trades     \vspace{0.2cm}
%   \item Max daily loss = 1\%            \vspace{0.2cm}
%   \item Max weekly Trades = 4 Trades    \vspace{0.2cm}
%   \item max weekly Loss = 3\%           \vspace{0.2cm}  
% \end{itemize}

\renewcommand{\arraystretch}{1.5} % table padding vertical space 
\setlength{\tabcolsep}{10pt} % table padding horizontal space

\subsection*{What Seperates Professional Traders From You?}
\vspace{0.3cm}
\begin{center}
  \small{Combinations of | [ Win/Loss Over 10 Trades ]} \\
  \small{With 1:1 Risk To Reward}
\end{center}

\begin{center}
\begin{tabular}{|c|c|c|}
  \hline
  WINS & LOSSES & WIN RATE \\ 
  \hline 
  10000 & NYKZN & 08:40AM \\  
  \hline
\end{tabular}
\end{center}
\vspace{0.1cm}


\begin{notesbox}
  \noindent | With this rules we can make our self in the right way for been consistent in the market.
\end{notesbox}


\footnote{Twitter [ @MR-5OBOT ]}
\end{document}
